Probability

### 2016-04-18 prob.tex
typos

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
A possible space of events is the set
$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
projection $\mathbb{0}$ and the unit projection
$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
possible post-measurement of a quantum system as follows: given some
arbitrary current quantum $\ket{\psi}$ to be measured, the event
$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
the event $\proj{1}$ states that the post-measurement state will be
$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
event $\mathbb{0}$ states that the post-measurement state will be the
empty state. Clearly irrespective of the current state $\ket{\psi}$
and irrespective of the particular experiment, the probability of
event $\mathbb{0}$ will always be 0 (it is an impossible event) and
the probability of event $\mathbb{1}$ will always be 1 (it is a
certain event). The probabilities attached to other events will depend
on the particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1 and the probability of event
$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
Hilbert space setup admits other possible spaces of events. For
example, another space of events could be
$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
$\proj{\ms}$ to the probability $\frac{1}{2}$.

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space $\Hilb$ and define the set of events $\qevents$ as all
linear combinations of \emph{projections} on $\Hilb$. Specifically,
let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on
$\Hilb$ with sum $\mathbb{1}$ and define the event space $\qevents$ to
be the linear span of these operators:
\[
\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
\]
Each quantum state $\ket{\psi}$ induces a probability measure
$\mu_\psi : \qevents \rightarrow [0,1]$ on the space of events
defined as follows:
\[
\mu_\psi(A) = \ip{\psi}{A\psi}
\]
Similarlly to the classical case, this probability measure satisfies:
\begin{itemize}
\item $\mu(\mathbb{1}) = 1$, and
\item for all $A \in \qevents$, we have $\mu(A^*A) \geq 0$.
\end{itemize}

>>>>

Consider the two-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
A possible space of events is the set
$\{ \mathbb{0}, \proj{0}, \proj{1}, \mathbb{1}\}$ consisting of the
projection operators $\proj{0}$ and $\proj{1}$ as well as the empty
projection $\mathbb{0}$ and the unit projection
$\mathbb{1} = \proj{0}+\proj{1}$. Each event is interpreted as a
possible post-measurement state of a quantum system as follows: given some
arbitrary current quantum $\ket{\psi}$ to be measured, the event
$\proj{0}$ states that the post-measurement state will be $\ket{0}$;
the event $\proj{1}$ states that the post-measurement state will be
$\ket{1}$; the event $\mathbb{1}$ states that the post-measurement
state will be a linear combination of $\ket{0}$ and $\ket{1}$; and the
event $\mathbb{0}$ states that the post-measurement state will be the
empty state. Clearly irrespective of the current state $\ket{\psi}$
and irrespective of the particular experiment, the probability of
event $\mathbb{0}$ will always be 0 (it is an impossible event) and
the probability of event $\mathbb{1}$ will always be 1 (it is a
certain event). The probabilities attached to other events will depend
on the particular state in question. If the state is $\ket{0}$, the
probability of event $\proj{0}$ is 1 and the probability of event
$\proj{1}$ is 0. If the state is $\ket{\ps}$, the probability of both
events $\proj{0}$ and $\proj{1}$ will be $\frac{1}{2}$. The same
Hilbert space setup admits other possible spaces of events. For
example, another space of events could be
$\{ \mathbb{0}, \proj{\ps}, \proj{\ms}, \mathbb{1}\}$. Using that
space of events, the state $\ket{0}$ maps both events $\proj{\ps}$ and
$\proj{\ms}$ to the probability $\frac{1}{2}$.

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
linear combinations of \emph{projections} on~$\Hilb$. Specifically,
let $P_1, P_2, \ldots, P_k$ be mutually orthogonal projections on
$\Hilb$ with sum $\mathbb{1}$ and define the event space $\qevents$ to
be the linear span of these operators:
\[
\qevents=\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} .
\]
Each quantum state $\ket{\psi}$ induces a probability measure
$\mu_\psi : \qevents \rightarrow [0,1]$ on the space of events
defined as follows:
\[
\mu_\psi(A) = \ip{\psi}{A\psi}
\]
Similarlly to the classical case, this probability measure satisfies:
\begin{itemize}
\item $\mu(\mathbb{1}) = 1$, and
\item for all $A \in \qevents$, we have $\mu(A^*A) \geq 0$.
\end{itemize}
